Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex
state of art modificado

\section{\uppercase{State of Art}}
\label{sec:state}
Our solutions is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines, several solutions have been presented.
The solution presented by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. 
This one continues without being integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. A runtime component to provide abstraction
and sharing of GPUs is presented in~\cite{becchi2012virtual}, which allows scheduling policies 
to isolate and share GPUs in a cluster for a set of applications. Our proposal uses a different 
approach employing virtual machines and a cloud computing environment to allow to share GPUs in a flexible way.
On the other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications. 
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

>>>>

\section{\uppercase{State of Art}}
\label{sec:state}
Our solutions is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines, several approaches have been implemented.
The solution presented by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. 
This one continues without being integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. A runtime component to provide abstraction
and sharing of GPUs is presented in~\cite{becchi2012virtual}, which allows scheduling policies 
to isolate and share GPUs in a cluster for a set of applications. Our proposal uses a different 
approach employing virtual machines and a cloud computing environment to allow to share GPUs in a flexible way.
On the other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications. 
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.
